biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-28 paper/PaperTRA/PaperTRA.Rmd
table 22

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1}Summary of the cycling potencial of intermodality scenario.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")
  # kableExtra::kable_styling(full_width = TRUE)

@@

```{r summary21}
summary2 = readRDS("load/TPtable_aml.Rds")

summary21 = summary2 %>%
  mutate(LTS = recode(Percursos, "seguro" = "safe", "direto" = "direct")) |> 
  select(Meta_ENMAC, LTS, Total, BUS, FERRY, RAIL, TRAM)

knitr::kable(summary21,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total",
                    "Bus", "Ferry", "Train", "Tram"),
      caption = "\\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.",
      format="latex",
      booktabs = TRUE)
  # kableExtra::column_spec(column = c(4:7), width = "6em")
  # kableExtra::kable_styling(full_width = TRUE)

@@

@@

summary22 = summary2 %>%
  mutate(LTS = recode(Percursos, "seguro" = "safe", "direto" = "direct")) |> 
  select(Meta_ENMAC, LTS, CO2eq_TP, CO_PT, PM10_PT, NOx_PT, VOC_PT, money_emissions_eur)
```

<!-- Tipo de Percurso   Meta ENMAC  Total   Barco   Comboio Autocarro   Metro superfície    CO~2~eq CO  PM10    NOx VOC Valorização monetária (€) -->

<!-- seguro 4%  192 214 5 167   169 984 4 163   12 900  8 593   17  1.9 27  0.8 1 424 620 -->

<!-- seguro 10% 224 152 5 594   197 857 5 042   15 659  20 627  42  4.6 65  2.0 3 430 552 -->

<!-- direto 4%  189 846 5 795   171 534 4 879   7 639   8 702   18  2.0 28  0.8 1 452 820 -->

<!-- direto 10% 219 511 6 263   198 373 5 806   9 069   20 793  42  4.7 66  1.9 3 487 282 -->

>>>>

<!-- For the full paper, explain that we had 3 scenarios, and describe them. But in this paper we focous on the intermodality one. -->

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1}Summary of the cycling potencial of intermodality scenario.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")

@@

```{r summary21}
summary2 = readRDS("load/summary2.Rds")

summary21 = summary2 %>%
  mutate(LTS = recode(LTS, "seguro" = "safe", "direto" = "direct")) |> 
  mutate(Estrategia = paste0(`Meta ENMAC`*100,"%")) |> 
  select(Estrategia, LTS, Total, Autocarro, Barco, Comboio, `Metro superfície`)

knitr::kable(summary21,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total",
                    "Bus", "Ferry", "Train", "Tram"),
      caption = "\\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(3:7), width = "4em")

@@

Table \ref{tab:summary22} is fine.

@@

summary22 = summary2 %>%
  mutate(LTS = recode(LTS, "seguro" = "safe", "direto" = "direct")) |> 
  mutate(Estrategia = paste0(`Meta ENMAC`*100,"%")) |> 
  mutate(Value = `Valorização monetária (€)`/1000) |> 
  select(Estrategia, LTS, CO2eq, CO, PM10, NOx, VOC, Value)

knitr::kable(summary22,
      digits = c(0,0,0,0,1,0,1,0),
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "CO2eq",
                    "CO", "PM10", "NOx", "VOC", "Value (k€)"),
      caption = "\\label{summary21}Summary of the avoided emmissions (ton/year) and corresponding monetization (thousand €) by replacing car trips with PT, in the second leg.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(3:7), width = "3.5em")
```

### 2023-09-28 paper/PaperTRA/PaperTRA.tex
table 22

Table \ref{tab:summary1} presents the LMA total daily trips, the cycling
combined with PT trips in the baseline scenario and corresponding
potential trips to achieve the national strategy targets (4\% and 10\%),
for different route profiles. For the cycling legs of the journey (first
and last legs), the environmental avoided emmissions and monetized
socio-environment benefits are also presented, resulting from replacing
car trips with cycling.

@@

\caption{\label{tab:summary1}\label{summary1old}Summary of the cycling potencial of intermodality scenario.}
\centering
\begin{tabular}[t]{llr>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
Target & Routing & Total trips & Baseline Cycling + PT & Potencial Cycling + PT & Avoided CO2eq (ton/yr) & SE Benefits for 10 years (thousand €)\\
\midrule
4\% & safe & 1 077 028 & 4 624 & 40 770 & 5 920 & 230 270\\
4\% & direct & 1 001 761 & 4 547 & 37 889 & 6 011 & 223 720\\
10\% & safe & 1 077 028 & 4 624 & 104 647 & 15 192 & 591 790\\
10\% & direct & 1 001 761 & 4 547 & 97 218 & 15 414 & 574 200\\
\bottomrule
\end{tabular}
\end{table}

This scenario unveils the potential of bicycles as a complementary mode
of PT, with the prospective to uptake the number of PT trips within the
LMA area by as much as 12\% (in addition to the 825,000 reported in the
mobility survey). These findings indicate that transferring car trips to
a combination of bicycle and PT could be nearly as substantial, if not
equally significant, as the shift towards bicycle-only trips.

@@

\begin{figure}
\includegraphics[width=1\linewidth,]{img/table2} \caption{Potencial de transferência estimado para cada modo de transporte público, bem como as estimativas de consumo de CO~2~eq evitado anualmente por transferência do automóvel.}\label{fig:summary2}
\end{figure}

>>>>

Table \ref{tab:summary1} presents the LMA total daily trips, the cycling
combined with PT trips in the baseline scenario and corresponding new
trips to achieve the national strategy targets (4\% and 10\%), for
different route profiles. For the cycling legs of the journey (first and
last legs), the environmental avoided emmissions and monetized
socio-environment benefits are also presented, resulting from replacing
car trips with cycling.

@@

\caption{\label{tab:summary1}\label{summary1}Summary of the cycling potencial of intermodality scenario.}
\centering
\begin{tabular}[t]{llr>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
Target & Routing & Total trips & Baseline Cycling + PT & Potencial Cycling + PT & Avoided CO2eq (ton/yr) & SE Benefits for 10 years (thousand €)\\
\midrule
4\% & safe & 1 077 028 & 4 624 & 40 770 & 5 920 & 230 270\\
4\% & direct & 1 001 761 & 4 547 & 37 889 & 6 011 & 223 720\\
10\% & safe & 1 077 028 & 4 624 & 104 647 & 15 192 & 591 790\\
10\% & direct & 1 001 761 & 4 547 & 97 218 & 15 414 & 574 200\\
\bottomrule
\end{tabular}
\end{table}

This scenario unveils the potential of bicycles as a complementary mode
of PT, with the potential to uptake the number of PT trips within the
LMA area by as much as 12\% (in addition to the 825,000 reported in the
mobility survey). These findings indicate that transferring car trips to
a combination of bicycle and PT could be nearly as substantial, if not
equally significant, as the shift towards bicycle-only trips.

@@

Table \ref{tab:summary21} shows something that doesn't make sense.

\caption{\label{tab:summary21}\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.}
\centering
\begin{tabular}[t]{ll>{\raggedleft\arraybackslash}p{4em}>{\raggedleft\arraybackslash}p{4em}>{\raggedleft\arraybackslash}p{4em}>{\raggedleft\arraybackslash}p{4em}>{\raggedleft\arraybackslash}p{4em}}
\toprule
Target & Routing & Total & Bus & Ferry & Train & Tram\\
\midrule
4\% & safe & 192 214 & 4 163 & 5 167 & 169 984 & 12 900\\
10\% & safe & 224 152 & 5 042 & 5 594 & 197 857 & 15 659\\
4\% & direct & 189 846 & 4 879 & 5 795 & 171 534 & 7 639\\
10\% & direct & 219 511 & 5 806 & 6 263 & 198 373 & 9 069\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:summary22} is fine.

\caption{\label{tab:summary22}\label{summary21}Summary of the avoided emmissions (ton/year) and corresponding monetization (thousand €) by replacing car trips with PT, in the second leg.}
\centering
\begin{tabular}[t]{ll>{\raggedleft\arraybackslash}p{3.5em}>{\raggedleft\arraybackslash}p{3.5em}>{\raggedleft\arraybackslash}p{3.5em}>{\raggedleft\arraybackslash}p{3.5em}>{\raggedleft\arraybackslash}p{3.5em}r}
\toprule
Target & Routing & CO2eq & CO & PM10 & NOx & VOC & Value (k€)\\
\midrule
4\% & safe & 8 593 & 17 & 1.9 & 27 & 0.8 & 1 425\\
10\% & safe & 20 627 & 42 & 4.6 & 65 & 2.0 & 3 431\\
4\% & direct & 8 702 & 18 & 2.0 & 28 & 0.8 & 1 453\\
10\% & direct & 20 793 & 42 & 4.7 & 66 & 1.9 & 3 487\\
\bottomrule
\end{tabular}
\end{table}
